Carbonate chemistry at Ny-Ålesund

### 2021-06-02 awipev-CO2.Rmd
Added plot stratification (deltas)

@@

@@

p <- tmp %>% 
  ggplot(aes(x=as.factor(depth), y = density)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(title = "Density vs depth", x = "Depth (m)", y= "Density") +
  scale_x_discrete(labels = c("0-4", "8-12")) +
  facet_wrap(vars(montht), scale = "free_y")
print(p)
```

>>>>

sal_delta_plt <- tmp_delta %>% 
  ggplot(aes(x=montht, y=sal_delta)) +
  labs(y = "Difference in median salinity", x = "Month") +
  geom_col(fill="blue") +
  geom_hline(yintercept = 0) +
  annotate("text", x = 1.5, y = 0.65, label = substitute("S"["surface"] ~ "> S"["deep"])) +
  annotate("text", x = 1.5, y = -0.9, label = substitute("S"["surface"] ~ "< S"["deep"])) +
  Mytheme(size_labs = 12) +
  theme(panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

@@

temp_delta_plt <- tmp_delta %>% 
  ggplot(aes(x=montht, y=temp_delta)) +
  labs(y = "Difference in median temperature", x = "Month") +
  geom_col(fill="blue") +
  geom_hline(yintercept = 0) +
  annotate("text", x = 1.5, y = 2.5, label = substitute("T"["surface"] ~ "> T"["deep"])) +
  annotate("text", x = 1.5, y = -2.5, label = substitute("T"["surface"] ~ "< T"["deep"])) +
  Mytheme(size_labs = 12) +
  theme(panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

@@

p <- tmp %>% 
  ggplot(aes(x=as.factor(depth), y = density)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(title = "Density vs depth", x = "Depth (m)", y= "Density") +
  scale_x_discrete(labels = c("0-4", "8-12")) +
  facet_wrap(vars(montht), scale = "free_y")
print(p)

den_delta_plt <- tmp_delta %>% 
  ggplot(aes(x=montht, y=den_delta)) +
  labs(y = "Difference in median density", x = "Month") +
  geom_col(fill="blue") +
  geom_hline(yintercept = 0) +
  annotate("text", x = 1.5, y = 0.1, label = substitute("D"["surface"] ~ "> D"["deep"])) +
  annotate("text", x = 1.5, y = -1.2, label = substitute("D"["surface"] ~ "< D"["deep"])) +
  Mytheme(size_labs = 12) +
  theme(panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

deltas <- sal_delta_plt / temp_delta_plt / den_delta_plt
ggsave(filename = "figures/deltas.png", plot = deltas, width = 15, height = 20, units = "cm")
```
